Invasive chameleons released from predation display more conspicuous colors

### 2022-01-22 ms_Nature.Rmd
I don't think we need any more detail on new analyses really. I think it's all clear, but I made reference to table S6 now.

Character release may reflect rapid evolutionary change, phenotypic plasticity or a combination of these processes [@RN19ms; @RN20ms]. Rapid evolutionary change results in local adaptation, whereby signals become more conspicuous to conspecifics in their local environment than in ancestral environments. Consistent with local adaptation, we found that Hawaiian chameleons were more conspicuous to other chameleons against their own (Hawaiian) background than against their ancestral Kenyan background, in both social contexts, although effect sizes for luminance were much larger than for chromatic contrast (Fig. \@ref(fig:figure4) and Supplementary Table 5; male-male contests: luminance ($dl$), $\beta$ = `r robust_localAdapt_DispBgrdAC[3,1]`, 95% CI = `r robust_localAdapt_DispBgrdAC[3,4]` to `r robust_localAdapt_DispBgrdAC[3,5]`, $F_{`r background_AC_Disp$df_num`,`r background_AC_Disp$df_denom`}$ = `r background_AC_Disp$Fstat`, *P* = `r p_value(background_AC_Disp[,6])`, chromatic ($dS$), $\beta$ = `r robust_DispBgrdCC[3,1]`, 95% CI = `r robust_DispBgrdCC[3,4]` to `r robust_DispBgrdCC[3,5]`, $F_{`r background_CC_Disp$df_num`,`r background_CC_Disp$df_denom`}$ = `r background_CC_Disp$Fstat`, *P* = `r p_value(background_CC_Disp[,6])`; courtship: luminance ($dl$), $\beta$ = `r robust_CourtshipAC[3,1]`, 95% CI = `r robust_CourtshipAC[3,4]` to `r robust_CourtshipAC[3,5]`, $F_{`r background_AC_Court$df_num`,`r background_AC_Court$df_denom`}$ = `r background_AC_Court$Fstat`, *P* = `r p_value(background_AC_Court[,6])`, chromatic ($dS$) $\beta$ = `r robust_CourtshipCC[3,1]`, 95% CI = `r robust_CourtshipCC[3,4]` to `r robust_CourtshipCC[3,5]`, $F_{`r background_CC_Court$df_num`,`r background_CC_Court$df_denom`}$ = `r background_CC_Court$Fstat`, *P* = `r p_value(background_CC_Court[,6]) `). These results are consistent with local adaptation, in which phenotypic plasticity, which can also evolve rapidly [@RN26ms], may also play a role.

>>>>

Character release may reflect rapid evolutionary change, phenotypic plasticity or a combination of these processes [@RN19ms; @RN20ms]. Rapid evolutionary change results in local adaptation, whereby signals become more conspicuous to conspecifics in their local environment than in ancestral environments. Consistent with local adaptation, we found that Hawaiian chameleons were more conspicuous to other chameleons against their own (Hawaiian) background than against their ancestral Kenyan background, in both social contexts, although effect sizes for luminance were much larger than for chromatic contrast (Fig. \@ref(fig:figure4) and Supplementary Tables 5 and 6; male-male contests: luminance ($dl$), $\beta$ = `r robust_localAdapt_DispBgrdAC[3,1]`, 95% CI = `r robust_localAdapt_DispBgrdAC[3,4]` to `r robust_localAdapt_DispBgrdAC[3,5]`, $F_{`r background_AC_Disp$df_num`,`r background_AC_Disp$df_denom`}$ = `r background_AC_Disp$Fstat`, *P* = `r p_value(background_AC_Disp[,6])`, chromatic ($dS$), $\beta$ = `r robust_DispBgrdCC[3,1]`, 95% CI = `r robust_DispBgrdCC[3,4]` to `r robust_DispBgrdCC[3,5]`, $F_{`r background_CC_Disp$df_num`,`r background_CC_Disp$df_denom`}$ = `r background_CC_Disp$Fstat`, *P* = `r p_value(background_CC_Disp[,6])`; courtship: luminance ($dl$), $\beta$ = `r robust_CourtshipAC[3,1]`, 95% CI = `r robust_CourtshipAC[3,4]` to `r robust_CourtshipAC[3,5]`, $F_{`r background_AC_Court$df_num`,`r background_AC_Court$df_denom`}$ = `r background_AC_Court$Fstat`, *P* = `r p_value(background_AC_Court[,6])`, chromatic ($dS$) $\beta$ = `r robust_CourtshipCC[3,1]`, 95% CI = `r robust_CourtshipCC[3,4]` to `r robust_CourtshipCC[3,5]`, $F_{`r background_CC_Court$df_num`,`r background_CC_Court$df_denom`}$ = `r background_CC_Court$Fstat`, *P* = `r p_value(background_CC_Court[,6]) `). These results are consistent with local adaptation, in which phenotypic plasticity, which can also evolve rapidly [@RN26ms], may also play a role.
